Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-31 ijar-npb-ms.tex
tweaks in Section 7

In Figure~\ref{fig:bridge-early},
test data of component type T3 is instead $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
and so earlier than expected.
Compared to Figure~\ref{fig:bridge-fitting},
posterior functioning intervals for T3 are wider between $t=1$ and $t=3.5$,
reflecting additional imprecision due to prior-data conflict.
For $t > 1$, it is clearly visible how $\ytnu{3}$ is halfway between $\ytzu{3}$ and $s_t^3/n_3 = 0$
(weights $\ntzu{3} = 4$ and $n_3 = 4$),
while $\ytnl{3}$ is one-fifth of $\ytzl{3}$
(weights $\ntzl{3} = 1$ and $n_3 = 4$).
Note that the posterior system functioning probability is constant for $t \in [1,2]$
because in that interval the prior functioning probability is constant
and there are no observed failures.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is now $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so observed failures are later than expected.
Here we see that for $t \in [2,4]$,
posterior functioning bounds for T3 are even wider than prior functioning bounds.
The width turns back to being half the prior width
only after the four failures.
The imprecision carries over to the system bounds,
where we see wider bounds as compared to the other two scenarios
especially between $t=2$ and $t=4$.  In particular, also note
that at the system level prior data conflict ceases after
$t \approx 2.6$, although the prior data conflict for the 
individual component type T3 extends well beyond $t=4$.  This 
demonstrates the power of this technique to identify prior
data conflict which is actually consequential at the system 
level, not just the component level --- in other words, for 
mission times $t>2.6$, we can diagnose that the prior data conflict 
need not be of concern for this system viewed as a whole.

@@

We also consider a simplified automotive brake system.
The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
the car brakes when at least one brake pad assembly is actuated.
All values for $\Phi \not\in \{0,1\}$ are given in Table~\ref{tab:brake-survsign}.
\begin{table}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
  \midrule
1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesystem}.
}
\label{tab:brake-survsign}
\end{table}
The system layout is depicted in Figure~\ref{fig:brakesystem},
together with prior and posterior sets of reliability functions for the four component types and the complete system.
Observed lifetimes from test data are indicated by tick marks in each of the four component type panels,
where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
Prior functioning probability bounds for M are based on
a Weibull cdf with shape $2.5$ and scales $6$ and $8$ for the lower and upper bound, respectively.
The prior bounds for P can be seen as the least committal bounds
derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.

For H, near-noninformative prior functioning probability bounds have been selected;
with the upper bound for P being approximately one for $t \le 5$ as well,
the prior upper system reliability bound for $t \le 5$ is close to one, too,
since the system can function on H and one of P1 -- P4 alone.
Note that the posterior functioning probability interval for M
is wide not only due to the limited number of observations,
but also because $\ntzu{\text{M}} = 8$ and the prior-data conflict reaction.

@@

It is also interesting to note that the prior data conflict 
which is consequential at the system level occurs over 
roughly the same range in $t$ as there is prior data 
conflict for component type P.  Indeed, this occurs despite there being 
prior data conflict in both M and C over much larger ranges, 
giving valuable insight into which prior requires further 
expert attention --- thus the technique avoids wasted time 
addressing prior data conflict in components which may not 
be relevant when propagated to the uncertainty in the whole system.

@@

>>>>

In Figure~\ref{fig:bridge-early},
test data of component type T3 is $\vec{t}^3 = (0.6, 0.7, 0.8, 0.9)$,
and so earlier than expected.
Compared to Figure~\ref{fig:bridge-fitting},
posterior functioning intervals for T3 are wider between $t=1$ and $t=3.5$,
reflecting additional imprecision due to prior-data conflict.
For $t > 1$, it is clearly visible how $\ytnu{3}$ is halfway between $\ytzu{3}$ and $s_t^3/n_3 = 0$
(weights $\ntzu{3} = 4$ and $n_3 = 4$),
while $\ytnl{3}$ is one-fifth of $\ytzl{3}$
(weights $\ntzl{3} = 1$ and $n_3 = 4$).
Note that the posterior system functioning probability is constant for $t \in [1,2]$
because in that interval the prior functioning probability is constant
and there are no observed failures.

@@

In Figure~\ref{fig:bridge-late}, 
test data of component type T3 is $\vec{t}^3 = (4.1, 4.2, 4.3, 4.4)$,
and so observed failures are later than expected.
Here we see that for $t \in [2,4]$,
posterior functioning bounds for T3 are even wider than prior functioning bounds.
The width turns back to being half the prior width
only after the four failures.
The imprecision carries over to the system bounds,
where we see wider bounds as compared to the other two scenarios
especially between $t=2$ and $t=4$. In particular, also note
%that at the system level prior data conflict ceases after
that at the system level posterior bounds are a subset of prior bounds after
$t = 2.6$, although prior-data conflict for the 
individual component type T3 extends well beyond $t=4$.  This 
demonstrates the power of this technique to identify prior-data conflict
which is actually consequential at the system 
level, not just the component level --- in other words, for 
mission times $t>2.6$, we can diagnose that the prior-data conflict 
need not be of elevated concern for this system viewed as a whole.
%mission times $t>2.6$, we see that posterior system reliability bounds
%are in line with prior expectations and so need not be of elevated concern. 
Nevertheless, the posterior system reliability bounds are wider than in the no-conflict case for $t \in [1, 4.4]$,
signalising the general need for caution in this scenario.

@@

We also consider a simplified automotive brake system.
The master brake cylinder (M) activates all four wheel brake cylinders (C1 -- C4),
which in turn actuate a braking pad assembly each (P1 -- P4).
The hand brake mechanism (H) goes directly to the brake pad assemblies P3 and P4;
the car brakes when at least one brake pad assembly is actuated.
All values for $\Phi \not\in \{0,1\}$ are given in Table~\ref{tab:brake-survsign}.
\begin{table}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
  \midrule
1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
0 & 1 & 1 & 1 & 0.62 & & 1 & 1 & 1 & 1 & 0.62 \\ 
0 & 1 & 1 & 2 & 0.92 & & 1 & 1 & 1 & 2 & 0.92 \\ 
0 & 1 & 2 & 1 & 0.75 & & 1 & 1 & 2 & 1 & 0.75 \\ 
0 & 1 & 2 & 2 & 0.97 & & 1 & 1 & 2 & 2 & 0.97 \\ 
0 & 1 & 3 & 1 & 0.88 & & 1 & 1 & 3 & 1 & 0.88 \\ 
   \bottomrule
\end{tabular}
\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesystem}.
}
\label{tab:brake-survsign}
\end{table}
The system layout is depicted in Figure~\ref{fig:brakesystem},
together with prior and posterior sets of reliability functions for the four component types and the complete system.
Observed lifetimes from test data are indicated by tick marks in each of the four component type panels,
where $n_\text{M}=5$, $n_\text{H}=10$, $n_\text{C}=15$, and $n_\text{P}=20$.
We assume $[\ntzl{\text{M}},\ntzu{\text{M}}] = [1,8]\ \forall t$,
and $[\nktzl, \nktzu] = [1,2]$ for $k \in \{\text{H, C, P}\}$ and all $t$.
Prior functioning probability bounds for M are based on
a Weibull cdf with shape $2.5$ and scales $6$ and $8$ for the lower and upper bound, respectively.
The prior bounds for P can be seen as the least committal bounds
derived from an expert statement of $\ytz{\text{P}} \in [0.5, 0.65]$ for $t=5$ only.
%
For H, near-noninformative prior functioning probability bounds have been selected;
with the upper bound for P being approximately one for $t \le 5$ as well,
the prior upper system reliability bound for $t \le 5$ is close to one, too,
since the system can function on H and one of P1 -- P4 alone.
Note that the posterior functioning probability interval for M
is wide not only due to the limited number of observations,
but also because $\ntzu{\text{M}} = 8$ and the prior-data conflict reaction.

@@

It is also interesting to note that the prior-data conflict 
which is consequential at the system level occurs over 
roughly the same range in $t$ as there is prior-data 
conflict for component type P.
%It is also interesting to note that the range in $t$
%for which posterior system reliability bounds are not a subset of prior bounds
%is roughly the same as there is prior-data conflict for component type P.
Indeed, this occurs despite there being 
prior-data conflict in both M and C over much larger ranges, 
giving valuable insight into which prior requires further 
expert attention --- thus the technique avoids wasted time 
addressing prior-data conflict in components which may not 
be relevant when propagated to the uncertainty in the whole system.

@@

Gero Walter was supported by the DINALOG project
``Coordinated Advanced Maintenance and Logistics Planning for the Process Industries'' (CAMPI).
